### 2024-11-02 paper/2-background.tex
Minor change

% other backends and other language
SpecTec also translates the DSL into Coq\cite{il2coq} for mathematical proofs
and it is also working on generating other artifacts such as test suites
required to the WebAssembly standization.
Moreover, some researches are ongoing to deploy SpecTec to mechanize other
languages \cite{p4-cherry-workshop}.

>>>>

% other backends and other language
SpecTec also translates the DSL into Coq for mathematical proofs ~\cite{il2coq}
and it is also working on generating other artifacts such as test suites
required to the WebAssembly standization.
% TODO: check any presentation about west, component model, or rust using SpecTec
Moreover, some researches are ongoing to deploy SpecTec to mechanize other
languages ~\cite{p4-cherry-workshop}.
